Persistence in functional analysis and a correction to a theorem of Morse

### 2021-06-15 main.tex
Change doc-class to springer and modify abstract

\immediate\write18{bibtex \jobname}
\documentclass{amsart}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{tikz-cd}
\usepackage[numbers,sort,compress]{natbib}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage[bookmarks=true,
bookmarksnumbered=true, breaklinks=true,
pdfstartview=FitH, hyperfigures=true,
plainpages=false, naturalnames=true,
colorlinks=true, pagebackref=true,
pdfpagelabels]{hyperref}
\hypersetup{
	linktocpage,
	colorlinks,
	citecolor=blue,
	linkcolor=blue,
	urlcolor=blue}
\usepackage[capitalize, noabbrev]{cleveref}
\usepackage{todo}

@@

% margins
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2.3in}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2.3in}
\calclayout

@@

\title[Persistence in functional analysis]{Persistence in functional analysis and a correction to a theorem of Morse}

% % Anibal
% \author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
% \address{Max Planck Institute for Mathematics, Bonn, Germany}
% \email{ammedmar@mpim-bonn.mpg.de}
% \address{Department of Mathematics, University of Notre, Notre Dame, IN, USA}
% \email{amedinam@nd.edu}

\date{\today}

\begin{abstract}
	During the 1930's Morse developed the theory of functional topology relating the critical set of a semi-continuous functional and the topology of its sublevel sets.
	Morse and Tompkins applied this body of work in the setting defined by Douglas' solution to Plateau's Problem, and proved with it their Unstable Minimal Surface Theorem.
	Many of the key insights of functional topology have been rediscovered in the study of persistent homology, with the notion of q-tameness being as central to functional topology as it is to persistence theory.
	With applications to geometry in mind, we present a modern treatment of local-connectivity of sublevel set filtrations, q-tameness of their associated persistence homology, and Morse inequalities.
	As a consequence of our analysis we identify and correct a gap in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
\end{abstract}

\maketitle
\tableofcontents
\input{introduction}
\input{persistence}
\input{inequalities}
\input{connectivity}
\input{surfaces}
\appendix
\input{vietoris}

>>>>

%\immediate\write18{bibtex \jobname}
\documentclass[nospthms, a4paper, final]{svjour3}
\setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}
\setlength{\textheight}{\dimexpr\pdfpageheight-2in}
\usepackage{mathptmx}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{tikz-cd}
\usepackage[numbers,sort,compress]{natbib}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage[bookmarks=true,
bookmarksnumbered=true, breaklinks=true,
pdfstartview=FitH, hyperfigures=true,
plainpages=false, naturalnames=true,
colorlinks=true, pagebackref=true,
pdfpagelabels]{hyperref}
\hypersetup{
	linktocpage,
	colorlinks,
	citecolor=blue,
	linkcolor=blue,
	urlcolor=blue}
\usepackage[capitalize, noabbrev]{cleveref}
\usepackage{todo}

@@

@@

\title{Persistence in functional analysis and a correction to a theorem of Morse}

\author{author1 \and author2 \and author3}

\institute{author1 \at where \\ \email{@} \and
	author2 \at where \\ \email{@} \and
	author3 \at where \\ \email{@} \and
}

\authorrunning{author1, author2, author3}

\maketitle

\begin{abstract}
	During the 1930's Morse developed the theory of functional topology relating the critical set of a semi-continuous functional and the topology of its sublevel sets.
	Morse and Tompkins applied this body of work to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
	In recent years, persistence homology has led to fast passed developments in both mathematical theory and practice within several fields including simplectic geometry, WHAT ELSE? and neuroscience. In this article, we present a modern account of Morse's functional topology from the point of view of persistence theory.
	We do so to allow for future applications of persistence techniques in functional analysis, as well as to correct a gap we identified in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
\end{abstract}

\tableofcontents
\input{introduction}
\input{persistence}
\input{inequalities}
\input{connectivity}
\input{surfaces}
\appendix
\input{vietoris}

### 2021-06-15 persistence.tex
Change doc-class to springer and modify abstract

In this section we present the theory of persistence as is used in connection with geometric questions.
A bridge build through filtrations by sublevel sets of real-valued functions.
For a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
An example of interest to us is given by volume functionals on moduli spaces of Riemannian manifolds.
For more examples please consult \cite{polterovich2020topological}.

>>>>

In this section we present the theory of persistence as is used in connection with geometric questions.
A bridge built through filtrations by sublevel sets of real-valued functions.
A class of examples directly related to the origin of this connection is that of functionals defined on the moduli spaces of Riemannian metrics on a manifold.
For more examples please consult \cite{polterovich2020topological} and for a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
